Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-02-13 manuscripts/paper-1/main.tex
Bibtex and Citiations are arranged

    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{GrievesInformationMirroringModel.png}
        \caption{Grieves Information Mirroring Model}
        \label{fig:GrievesInformationMirroringModel}
        \cite{GrievesPLMBook}
    \end{figure}

@@

    \subsection*{Literature Result}
    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results. After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English. 
    After the third filtering process, 9 dissertations passed and the rest is rejected.

@@

    Important findings are the following;
    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component.
        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
    \end{itemize}

@@

    \subsection{Second criterion: Completeness}
    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete \cite{OxfordDictionary}.
    We'll use the adjectival form which describes the word "complete" as having all the necessary or appropriate parts.
    One should first analyze and synthesize the real system to identify the subsystems and related systems in the supra-system before evaluating the completeness of the digital twin. 
    Completeness can be assessed after analysis and synthesis by contrasting the subsystems of the real world with those in the digital twin.

@@

    \subsection{Fourth criterion: Efficiency}
    Efficiency refers to the quality of being efficient, and efficiency can be explained as achieving maximum productivity with minimum wasted effort or expense. 
    The concept of efficiency is tightly coupled with productivity, which refers to the quality of being productive. The word productive can be explained as producing or being able to produce large amounts of goods \cite{OxfordDictionary}.
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired. Goods of the digital twin are nothing but information, 
    which Grieves first indicated with this Information Mirror Model \cite{GrievesPLMBook}. So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.

@@

    \subsection{Fifth criterion: Evolvability}
    TODO CITE
    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability. Another term used to describe the response to changes in the environment is adaptability. 
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. In contrast, evolvable systems undergo definite changes in their structures.  
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout depending on the user's hardware. 
    As we have seen in CITE, the update method shows that digital twins are evolvable systems,
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis, reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed.

>>>>

    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{GrievesInformationMirroringModel.png}
        \caption{Grieves Information Mirroring Model}\label{fig:GrievesInformationMirroringModel}
        \cite{GrievesPLMBook}
    \end{figure}

@@

    \subsection*{Literature Result}
    First filtering was done for the search term `digital twin quality', meanwhile GS gave 41 different results, and SCP gave only 3 results. After the second filtering process, 3 duplications and 31 different results were found and 10 dissertations were not in English. 
    After the third filtering process, 9 dissertations passed and the rest is rejected.

@@

    Important findings are the following;
    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin~\cite{Shcherba}.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, 
        the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component~\cite{ZHANGEVALUATIONMETHOD}.
        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed~\cite{ZHANGUPDATEMETHOD}.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated~\cite{QualityMonitoringofCoupledDigitalTwins}.
    \end{itemize}

@@

    \subsection{Second criterion: Completeness}
    Complete can be used as an adjective, attribute, or verb with an object. Completeness is a word that is derived from complete~\cite{OxfordDictionary}.
    We'll use the adjectival form which describes the word `complete' as having all the necessary or appropriate parts.
    One should first analyze and synthesize the real system to identify the subsystems and related systems in the supra-system before evaluating the completeness of the digital twin. 
    Completeness can be assessed after analysis and synthesis by contrasting the subsystems of the real world with those in the digital twin.

@@

    \subsection{Fourth criterion: Efficiency}
    Efficiency refers to the quality of being efficient, and efficiency can be explained as achieving maximum productivity with minimum wasted effort or expense. 
    The concept of efficiency is tightly coupled with productivity, which refers to the quality of being productive. The word productive can be explained as producing or being able to produce large amounts of goods~\cite{OxfordDictionary}.
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired. Goods of the digital twin are nothing but information, 
    which Grieves first indicated with this Information Mirror Model~\cite{GrievesPLMBook}. So to assess the efficiency, one should inspect the sinks and sources of the digital twin system, to identify the waste, expense and productivity.

@@

    \subsection{Fifth criterion: Evolvability}
    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional structure is referred to as evolvability. Another term used to describe the response to changes in the environment is adaptability. 
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. In contrast, evolvable systems undergo definite changes in their structures.  
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout depending on the user's hardware. 
    As we have seen in~\cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems,
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis, reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed.
